### 2020-04-25 generated/paper_EN.Rmd
Fix typo

## Operational system
```{r sistema, echo=FALSE}
v <- as.matrix(R.Version())
kable(v, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```

## Packages
```{r pacotes, echo=FALSE}
p <- matrix(
      c(
        "caret", as.character(packageVersion("caret")),
        "cowplot",as.character(packageVersion("cowplot")),
        "dplyr", as.character(packageVersion("dplyr")),
        "factoextra", as.character(packageVersion("factoextra")),
        "gdata", as.character(packageVersion("gdata")),
        "ggplot2", as.character(packageVersion("ggplot2")),
        "gridExtra",as.character(packageVersion("gridExtra")),
        "kableExtra",as.character(packageVersion("kableExtra")),
        "knitr",as.character(packageVersion("knitr")),
        "pastecs",as.character(packageVersion("pastecs")),
        "purrr", as.character(packageVersion("purrr")),
        "questionr", as.character(packageVersion("questionr")),
        "reshape2", as.character(packageVersion("reshape2")),
        "tidyr", as.character(packageVersion("tidyr")),
        "tidyverse", as.character(packageVersion("tidyverse"))
      ),
      ncol = 2,
      byrow=TRUE
    )
kable(p, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```
\newpage

>>>>

## Operational system
```{r system, echo=FALSE}
v <- as.matrix(R.Version())
kable(v, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```

## Packages
```{r packages, echo=FALSE}
p <- matrix(
      c(
        "caret", as.character(packageVersion("caret")),
        "cowplot",as.character(packageVersion("cowplot")),
        "dplyr", as.character(packageVersion("dplyr")),
        "factoextra", as.character(packageVersion("factoextra")),
        "gdata", as.character(packageVersion("gdata")),
        "ggplot2", as.character(packageVersion("ggplot2")),
        "gridExtra",as.character(packageVersion("gridExtra")),
        "kableExtra",as.character(packageVersion("kableExtra")),
        "knitr",as.character(packageVersion("knitr")),
        "pastecs",as.character(packageVersion("pastecs")),
        "purrr", as.character(packageVersion("purrr")),
        "questionr", as.character(packageVersion("questionr")),
        "reshape2", as.character(packageVersion("reshape2")),
        "tidyr", as.character(packageVersion("tidyr")),
        "tidyverse", as.character(packageVersion("tidyverse"))
      ),
      ncol = 2,
      byrow=TRUE
    )
kable(p, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```
\newpage

### 2020-04-25 generated/paper_PT.Rmd
Fix typo

## Sistema operacional
```{r sistema, echo=FALSE}
v <- as.matrix(R.Version())
kable(v, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```

## Pacotes utilizados
```{r pacotes, echo=FALSE}
p <- matrix(
      c(
        "caret", as.character(packageVersion("caret")),
        "cowplot",as.character(packageVersion("cowplot")),
        "dplyr", as.character(packageVersion("dplyr")),
        "factoextra", as.character(packageVersion("factoextra")),
        "gdata", as.character(packageVersion("gdata")),
        "ggplot2", as.character(packageVersion("ggplot2")),
        "gridExtra",as.character(packageVersion("gridExtra")),
        "kableExtra",as.character(packageVersion("kableExtra")),
        "knitr",as.character(packageVersion("knitr")),
        "pastecs",as.character(packageVersion("pastecs")),
        "purrr", as.character(packageVersion("purrr")),
        "questionr", as.character(packageVersion("questionr")),
        "reshape2", as.character(packageVersion("reshape2")),
        "tidyr", as.character(packageVersion("tidyr")),
        "tidyverse", as.character(packageVersion("tidyverse"))
      ),
      ncol = 2,
      byrow=TRUE
    )
kable(p, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```
\newpage

>>>>

## Sistema operacional
```{r system, echo=FALSE}
v <- as.matrix(R.Version())
kable(v, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```

## Pacotes utilizados
```{r packages, echo=FALSE}
p <- matrix(
      c(
        "caret", as.character(packageVersion("caret")),
        "cowplot",as.character(packageVersion("cowplot")),
        "dplyr", as.character(packageVersion("dplyr")),
        "factoextra", as.character(packageVersion("factoextra")),
        "gdata", as.character(packageVersion("gdata")),
        "ggplot2", as.character(packageVersion("ggplot2")),
        "gridExtra",as.character(packageVersion("gridExtra")),
        "kableExtra",as.character(packageVersion("kableExtra")),
        "knitr",as.character(packageVersion("knitr")),
        "pastecs",as.character(packageVersion("pastecs")),
        "purrr", as.character(packageVersion("purrr")),
        "questionr", as.character(packageVersion("questionr")),
        "reshape2", as.character(packageVersion("reshape2")),
        "tidyr", as.character(packageVersion("tidyr")),
        "tidyverse", as.character(packageVersion("tidyverse"))
      ),
      ncol = 2,
      byrow=TRUE
    )
kable(p, booktabs = T) %>%
    kable_styling(latex_options = c("HOLD_position"))
```
\newpage
